\documentclass[../../../main.tex]{subfiles}
\graphicspath{{\subfix{../../../res/}}}
\begin{document}

Another good method for classification and regression tasks, \acrfull{rf}, is a robust and versatile learning method. It operated by creating a multitude of decision trees during training, then outputting the class - for classification, the mode of the classes - for regression, the mean prediction (for each individual tree).
This technique enhance the predictive accuracy and overcomes the overfitting problem associated with single decision tree.
Its strength lies in its ability to handle large datasets without extensive data preprocessing requirements. 

One student focused on different \acrfull{rf} algorithm, including \acrfull{rf} using the \acrfull{smote} or Boosted \acrshort{rf}. It showed interesting premises with from a predictive standpoint. \cite{lee_machine_2019}
\begin{table}[H]
    \centering
    \caption{\acrfull{acr} results of the classifiers used in this study\cite{lee_machine_2019}}
    \begin{tabular}{|c|c|}
        \hline
        \textbf{Model} & \textbf{AUC}\\
        \hline
        \acrfull{rf} & 0.986 \\
        \hline
        \acrshort{rf} + \acrshort{smote} & 0.986\\
        \hline
        Boosted \acrshort{rf} & 0.988 \\
        \hline
    \end{tabular}
    \label{tab:auc_values_lee}
\end{table}

Boosted \acrshort{rf} is an advanced version of \acrshort{rf} using boosting. Boosting is a method of sequentially improving a model's accuracy by focusing on previous models' misclassification. The algorithm starts with a base \acrshort{rf} and iteratively adds more trees. Each new tree trained on the residuals of the previous ensemble of trees. This process continues until a specified number of trees are added, or no significant improvement is observed.

\acrfull{smote} is a powerful approach used in \acrshort{ml}. Primarily used when dealing with imbalanced datasets (datasets where one class, usually the class of interest, is underrepresented compared to other classes). These datasets lead to poorly performing and biased models.
However, it's important to apply \acrshort{smote} carefully, as it can introduce noise into the dataset. This approach is best used with a large dataset and when the minority class is underrepresented in order to create meaningful synthetic samples.

\end{document}